Named Entity Recognition as Structured Prediction

### 2012-11-09 doc/report/paper.tex
++++methods

\begin{table}[h!]
\scriptsize
\begin{tabular}{| l | l |}
\hline
\bf Named Entity Type & \bf Example \\
\hline
Person Names & Greta Garbo, John, Mary \\
Organisations& Benetton, Coca-Cola Gmbh\\
Locations&  Paris, Australia, Bristol\\
Miscellaneous& World Cup 2014\\
 Date Expression& 01-02-2012, January, 6th, 1998 \\
Time Expression & 10 p.m.\\
Monetary Value &  \$15, \textsterling 100    \\
Percent &   30\% \\
\hline
\end{tabular}
\caption{NE Examples}
\label{table:NETypes}
\end{table}

@@

For statistical approaches, supervised-learning is the most commonly method applied in \emph{NER}. 
There are unsupervised methods, but they cannot compete with SL applications yet.
Prominent algorithms in NER include maximum entropy models,

neural network

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro} and 
the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on the system of \cite{strlearn} that won the challenge for English and German in 2003.

>>>>

\begin{table}[h!]
\scriptsize
\begin{tabular}{| l | l |}
\hline
\bf Named Entity Type & \bf Example \\
\hline
Person Names & Greta Garbo, John, Mary \\
Organisations& Benetton, Coca-Cola Gmbh\\
Locations&  Paris, Australia, Bristol\\
Miscellaneous& World Cup 2014, Italien\\
 Date Expression& 01-02-2012, January, 6th, 1998 \\
Time Expression & 10 p.m.\\
Monetary Value &  \$15, \textsterling 100    \\
Percent &   30\% \\
\hline
\end{tabular}
\caption{NE Examples}
\label{table:NETypes}
\end{table}

@@

For statistical approaches, supervised-learning is the most commonly method applied in \emph{NER}. 
There are unsupervised methods, but they cannot compete with SL applications yet.
Among the most prominent algorithms in NER are maximum entropy models. For CoNLL 2003, five of the sixteen systems
used this statistical learning method; three of them in isolation and they seem to be a very suitable choice for this task, since the three highest results in 
English and the two highest results in German were obtained by systems that employed this approach \cite{TjongKimSang:2003:ICS:1119176.1119195}.
The best system in both German and English \cite{Florian:2003:NER:1119176.1119201} used a combination of classifiers: a robust linear classifier, a maximum entropy, a transformation-based learning, and a hidden Markov model which are connected through a linear interpolation of the classifiers’ % combination scheme
class probability distribution. Particular importance is also assigned to creating a rich feature space, also including a gazetteer feature. 
This system gains a precision of 88.99\% on the English test set and  83.87\% on the German one. 
neural network

\subsection{CoNLL Data and Baseline Performance}
The training and test data for Spanish \& Dutch was taken from the \emph{CoNLL Shared Task 2002} \cite{tksintro} and 
the \emph{CoNLL Shared Task 2003} \cite{TjongKimSang:2003:ICS:1119176.1119195} provided the one for English \& German.
The ConNLL shared tasks are organised challenges, where the organisers propose a task and provide the participants with the
training and test data. 
In 2002 and 2003, the task was Named Entity Recognition. 
In both years, the baseline rate for the individual languages was produced by a system, that had a unique class in the training data. 
In case that a phrase was part of more than one entity, the system would choose the longest one \cite{TjongKimSang:2003:ICS:1119176.1119195}. 
Table \ref{table:Base} shows the baseline for the four different languages.  
The data is annotated with part-of-speech tags and named-entity tags, as well as Bio-tags that indicate the position in the Named Entity. %put in ``tokenized, chunked''
Our approach is based on the system of \cite{strlearn} that won the challenge for Spanish and Dutch in 2002.
